---
title: "STAT 331 Portfolio"
author: "Scarlet Kwan"
format: html 
embed-resources: true
layout: margin-left
editor: visual
execute: 
  eval: false
  echo: true
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an B.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from Lab or Challenge assignments where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2).

## Working with Data

**WD-1: I can import data from a *variety* of formats (e.g., csv, xlsx, txt, etc.).**

-   `csv` Example 1

```{r}
#| label: wd-1-csv-1
# Lab 2 Question 1
surveys <- read_csv(here::here("week 2","lab 2", "surveys.csv"))

```

-   `csv` Example 2

```{r}
#| label: wd-1-csv-2
# Lab 3 Question 2
evals <- read_csv(here::here("week 3", "lab 3", "teacher_evals.csv"))

```

-   `xlsx`

```{r}
#| label: wd-1-xlsx
# PA 4 Data Import
library(tidyverse)
library(readxl)
military <- read_xlsx("gov_spending_per_capita.xlsx",
                      sheet = "Share of Govt. spending",
                      skip  = 7,
                      n_max = 190,
                      na = c(". .", "xxx", "..")
                      )
```

**WD-2: I can select necessary columns from a dataset.**

-   Example selecting specified columns

```{r}
#| label: wd-2-ex-1
# Lab 3 Question 8
teacher_evals_clean |>
  filter(if_any(everything(), is.na)) |>
  select(teacher_id, course_id, everything())
```

-   Example removing specified columns

```{r}
#| label: wd-2-ex-2
# Lab 7 Question 3
fish |>
  group_by(year, section, trip) |>
  summarise(across(everything(), ~sum(is.na(.x)))) |>
  ungroup() |>
  pivot_longer(
    -c(year, section, trip),
    names_to = "variable",
    values_to = "number_of_missing_values") |>
  filter(number_of_missing_values > 0) |>
  ggplot(mapping = aes(x = as.factor(trip), y = number_of_missing_values, fill = variable)) +
  geom_col() +
  facet_grid(year ~ section)+
  labs(
    x = "Trip",
    y = "Number of Missing Values",
    fill = "Variable",
    title = "Frequency and Missing Data Patterns by Year, Section, and Trip"
  )

```

-   Example selecting columns based on logical values (e.g., `starts_with()`, `ends_with()`, `contains()`, `where()`)

```{r}
#| label: wd-2-ex-3
# Lab 5
annabel <- person |>
  filter(address_street_name == ("Franklin Ave"),
         str_detect(name, pattern = "^Annabel"))
```

**WD-3: I can filter rows from a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-3-numeric-ex-1
# Lab 3 Question 5
teacher_evals_clean <- evals |>
  rename(sex = gender)|>
  filter(no_participants >= 10)|>
  mutate(
    teacher_id = as.character(teacher_id),
    across(c(academic_degree, seniority, sex), as.factor)
  )|>
  select(course_id, teacher_id, question_no, no_participants, resp_share,
         SET_score_avg, percent_failed_cur, academic_degree, seniority, sex)
```

-   Numeric Example 2

```{r}
#| label: wd-3-numeric-ex-2
# Lab 7 Question 2
fish |>
  summarise(across(everything(), ~sum(is.na(.x)))) |>
  pivot_longer(
    everything(),
    names_to = "variable",
    values_to = "number_of_missing_values") |>
  filter(number_of_missing_values > 0)
```

-   Character Example 1 (any context)

```{r}
#| label: wd-3-character
# Lab 5
annabel <- person |>
  filter(address_street_name == ("Franklin Ave"),
         str_detect(name, pattern = "^Annabel"))
```

-   Character Example 2 (example must use functions from **stringr**)

```{r}
#| label: wd-3-string
# Lab 5
gym_person <- joint_data2 |>
  filter(membership_status == ("gold"),
         str_detect(id, pattern = "^48Z"),
         str_detect(plate_number, pattern = "H42W"))
```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-3-date
# Lab 5 (Revised so the date is a date and not a string)
  crime_scene_report <- crime_scene_report |>
    filter(date == ymd("20180115"),
           city == ("SQL City"),
           type == ("murder"))
```

**WD-4: I can modify existing variables and create new variables in a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-4-numeric-ex-1
# Lab 10 Question 2
results |> 
  enframe(name = NULL, value = "correct_babies") |>     
  count(correct_babies) |>                                
  mutate(proportion = n / sum(n)) |>               
  gt() |>                                         
  fmt_percent(                                     
    columns = proportion,
    decimals = 2
  ) |> 
  tab_header(
    title = "Proportion of Correct Baby Returns in 10000 Simulations"
  )


```

-   Numeric Example 2

```{r}
#| label: wd-4-numeric-ex-2
#challenge 7 question 1

fish <- fish|>
  mutate(length_cm = length/10)

```

-   Factor Example 1 (renaming levels)

```{r}
#| label: wd-4-factor-ex-1
# Lab 4 Question 4
ca_childcare <- ca_childcare |> 
  mutate(county_name = str_remove(county_name, " County"),
         region = fct_collapse(county_name,
    "Superior California" = superior_counties,
    "North Coast" = north_coast_counties,
    "San Francisco Bay Area" = san_fran_counties,
    "Northern San Joaquin Valley" = n_san_joaquin_counties,
    "Central Coast" = central_coast_counties,
    "Southern San Joaquin Valley" = s_san_joaquin_counties,
    "Inland Empire" = inland_counties,
    "Los Angeles" = la_county,
    "Orange County" = orange_county,
    "San Diego–Imperial" = san_diego_imperial_counties),
    region = fct_relevel(region,
    "San Francisco Bay Area",
    "Orange County",
    "Los Angeles County",
    "Northern San Joaquin Valley",
    "Central Coast",
    "Inland Empire",
    "Superior California",
    "Southern San Joaquin Valley",
    "San Diego–Imperial",
    "North Coast"))
```

-   Factor Example 2 (reordering levels)

```{r}
#| label: wd-4-factor-ex-2
# Lab 4 Question 7 
plot <- ca_childcare |>
  pivot_longer(cols = c(mfcc_infant,
                        mfcc_toddler,
                        mfcc_preschool),
              names_to = "age_group",
              values_to = "price") |>
  mutate(age_group = case_when(
    age_group == "mfcc_infant" ~ "Infant",
    age_group == "mfcc_toddler" ~ "Toddler",
    age_group == "mfcc_preschool" ~ "Preschool"),
    age_group = factor(age_group, levels = c("Infant", "Toddler", "Preschool")),
    region = fct_reorder2(region, study_year, price))

```

-   Character (example must use functions from **stringr**)

```{r}
#| label: wd-4-string
# Lab 8 Question 3
plot_function <- function(df, x, y) {
  
  
  ggplot(df, aes(x = {{ x }}, y = {{ y }}, color = {{ y }})) +
    geom_point() +
    labs(
      x = str_replace_all(rlang::as_label(rlang::enquo(x)),  "_", " "),
      y = str_replace_all(rlang::as_label(rlang::enquo(y)),  "_", " "),
      title = paste("Relationship between",
                    str_replace_all(rlang::as_label(rlang::enquo(x)),  "_", " "),
                    "and",
                    str_replace_all(rlang::as_label(rlang::enquo(y)),  "_", " ")),
      color = str_replace_all(rlang::as_label(rlang::enquo(y)),  "_", " ")
      )
   
}

```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-4-date
# Lab 5 (Revised to mutate and then filter date)
crime_scene_report <- crime_scene_report |>
  mutate(date = ymd(date)) |>
  filter(date == "2018-01-15",
         city == "SQL City",
         type == "murder")
```

**WD-5: I can use mutating joins to combine multiple dataframes.**

-   `left_join()` Example 1

```{r}
#| label: wd-5-left-ex-1
# Lab 5 (Revised to change inner_join() to left_join())
drivers_license |>
  left_join(person, by = join_by("id" == "license_id")) |>
  left_join(facebook_event_checkin, by = join_by("id.y" == "person_id")) |>
  filter(car_make == "Tesla",
         car_model == "Model S",
         hair_color == "red",
         gender == "female", 
         event_name == "SQL Symphony Concert") |>
  select(id.y)
```

-   `right_join()` Example 1

```{r}
#| label: wd-5-right
# Lab 4 Question 3 (Revised to use a right_join())
ca_childcare <- ca_childcare |>
  right_join(
    tax_rev,
    by = join_by(county_name == entity_name, study_year == year)
  )
```

-   `left_join()` **or** `right_join()` Example 2

```{r}
#| label: wd-5-left-right-ex-2
# Lab 5 (Revised to change inner_join() to left_join())
get_fit_now_member |>
  left_join(person, join_by("person_id" == "id")) |>
  left_join(drivers_license, by = join_by("license_id" == "id")) |>
  filter(
    membership_status == "gold",
    str_detect(id, "^48Z"),
    str_detect(plate_number, "H42W")
  ) |>
  select(name.x, person_id)
```

-   `inner_join()` Example 1

```{r}
#| label: wd-5-inner-ex-1
# Lab 4 Question 2
ca_childcare <- childcare_costs |>
  inner_join(x = counties,
             y = childcare_costs,
             by = join_by(county_fips_code))  |>
  filter( state_abbreviation == "CA")
```

-   `inner_join()` Example 2

```{r}
#| label: wd-5-inner-ex-2
# Lab 5
hire_joint <- inner_join(drivers_license, person, by = join_by("id" == "license_id"))
```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

-   `semi_join()`

```{r}
#| label: wd-6-semi
# Lab 5 (Revised to use a semi_join())
interview |>
  semi_join(
    person |> filter(address_street_name == "Franklin Ave",
                     str_detect(name, "^Annabel")),
    by = join_by(person_id == id)
  ) |>
  pull(transcript)
```

-   `anti_join()`

```{r}
#| label: wd-6-anti
# Lab 5 Revised code to check to see who didn't go to the concert to check suspect. 
person |> 
  anti_join(facebook_event_checkin, by = join_by(id == person_id))
```

**WD-7: I can pivot dataframes from long to wide and visa versa**

-   `pivot_longer()`

```{r}
#| label: wd-7-long
# Lab 4 Question 7
plot <- ca_childcare |>
  pivot_longer(cols = c(mfcc_infant,
                        mfcc_toddler,
                        mfcc_preschool),
              names_to = "age_group",
              values_to = "price") |>
  mutate(age_group = case_when(
    age_group == "mfcc_infant" ~ "Infant",
    age_group == "mfcc_toddler" ~ "Toddler",
    age_group == "mfcc_preschool" ~ "Preschool"),
    age_group = factor(age_group, levels = c("Infant", "Toddler", "Preschool")),
    region = fct_reorder2(region, study_year, price))
```

-   `pivot_wider()`

```{r}
#| label: wd-7-wide
# Lab 4 Question 5
med_income <- ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(region, study_year) |>
  summarise(median_income = median(mhi_2018, na.rm = TRUE), .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median_Household_Income_")|>
   arrange(desc(Median_Household_Income_2018))
```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

The following assignments satisfy the above criteria:

-   Example 1: Challenge 1
-   Example 2: Lab 1
-   Example 3: Lab 2
-   Example 4: Challenge 2
-   Example 5: Challenge 3

**R-2: I can write well documented and tidy code.**

-   Example of **ggplot2** plotting

```{r}
#| label: r-2-1
# Challenge 3 Question 2
ggplot(new_teacher_eval, aes(x = sen_level, fill = set_level)) +
  geom_bar(position = "fill",stat = "count")+
  labs(
    title = "Level of SET Ratings by Instructor Seniority",
    x = "Years of Experience",
    y = "", 
    fill = "Evaluation level")+
  scale_y_continuous(labels = scales::percent)+
  scale_fill_manual(values = c("excellent" = "mediumpurple1", "standard" = "tan"))+
  theme(legend.position = "top")
```

-   Example of **dplyr** pipeline

```{r}
#| label: r-2-2
# Lab 4 Question 5
med_income <- ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(region, study_year) |>
  summarise(median_income = median(mhi_2018, na.rm = TRUE), .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median_Household_Income_")|>
   arrange(desc(Median_Household_Income_2018))
```

-   Example of function formatting

```{r}
#| label: r-2-3
# Lab 8 Question 4
style_plot <- function(plot, theme_fn = theme_bw(), palette = RColorBrewer::brewer.pal(8, "Accent"), aesthetic = "fill") {
  
  if (!aesthetic %in% c("color", "fill")) {
    stop()
  }

  styled_plot <- plot + theme_fn
  
  if (aesthetic == "color") {
    styled_plot <- styled_plot + scale_color_manual(values = palette)
  } else {
    styled_plot <- styled_plot + scale_fill_manual(values = palette)
  }
  
  return(styled_plot)
}
```

**R-3: I can write robust programs that are resistant to changes in inputs.**

-   Example (any context)

```{r}
#| label: r-3-example
#Lab 7 Question 4
rescale_01 <- function(x){
  
  if (!is.numeric(x)) {
    stop()
  }
  
  if (length(x) <= 1) {
    stop()
  }

  y <- range(x, na.rm = TRUE)
  
  x = (x -y[1]) / (y[2] - y[1])
}

```

-   Example (function stops)

```{r}
#| label: r-3-function-stops
# Challenge 7 Question 2
change_impossible_measurements <- function(v, min_value, max_value) {
  if (!is.numeric(v)) {
    stop()}

  if (!is.numeric(min_value) || !is.numeric(max_value)) {
    stop()}

  if (min_value > max_value) {
    stop()}
  
  case_when(
    v < min_value ~ NA,
    v > max_value ~ NA,
    TRUE ~ v)
}
```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a *variety* of variable types (e.g., numeric, character, factor, date)**

-   At least two numeric variables

```{r}
#| label: dvs-1-num
# Lab 4 Question 8
ggplot(ca_childcare, aes(x = mhi_2018, 
                         y = mfcc_infant)) +
  geom_point(alpha = 0.5, color = "green") +
  geom_smooth(method = "lm", color = "pink") +
  labs(
    title = "Relationship between median household income and infant childcare prices in California",
    x = "Median household income in 2018 ($)",
    y = "Median weekly price for infant care ($)") 

```

-   At least one numeric variable and one categorical variable

```{r}
#| label: dvs-2-num-cat
# Lab 2 Question 16 (revised)
ggplot(data = surveys,
       mapping = aes( x = species, y = weight)) +
  geom_jitter(height = 0.25, color = "darkgreen", alpha = 0.125)+
  geom_boxplot(outlier.shape = NA)+
  labs( x = "Weight (g)", y = NULL, title = "Rodent weight by species", subtitle = "Species")+
  theme(axis.text.x = element_text(angle = 45),
        axis.text.y = element_text(color = "black"), 
        plot.title = element_text(face = "bold"))
```

-   At least two categorical variables

```{r}
#| label: dvs-2-cat
# Lab 7 Question 3
fish |>
  group_by(year, section, trip) |>
  summarise(across(everything(), ~sum(is.na(.x)))) |>
  ungroup() |>
  pivot_longer(
    -c(year, section, trip),
    names_to = "variable",
    values_to = "number_of_missing_values") |>
  filter(number_of_missing_values > 0) |>
  ggplot(mapping = aes(x = as.factor(trip), y = number_of_missing_values, fill = variable)) +
  geom_col() +
  facet_grid(year ~ section)+
  labs(
    x = "Trip",
    y = "Number of Missing Values",
    fill = "Variable",
    title = "Frequency and Missing Data Patterns by Year, Section, and Trip"
  )
```

-   Dates (time series plot)

```{r}
#| label: dvs-2-date
# Lab 4 Question 7
ggplot(plot, mapping = aes(x = study_year, y = price, color = region))+
  geom_point(alpha = 0.3, size = 1) + 
  geom_smooth(
    size = 0.8) +
  facet_wrap(~ age_group, ncol = 3) +
  labs(
    title = "Weekly Median Price for Center_based Childcare ($)",
    x = "Study Year",
    y = "",
    color = "Region")+
  theme(
    plot.title = element_text(size = 10),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 6),
    legend.position = "right",
    aspect.ratio = 1)
```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

-   I can modify my plot theme to be more readable

```{r}
#| label: dvs-2-ex-1
# Lab 4 Question 7
ggplot(plot, mapping = aes(x = study_year, y = price, color = region))+
  geom_point(alpha = 0.3, size = 1) + 
  geom_smooth(
    size = 0.8) +
  facet_wrap(~ age_group, ncol = 3) +
  labs(
    title = "Weekly Median Price for Center_based Childcare ($)",
    x = "Study Year",
    y = "",
    color = "Region")+
  theme(
    plot.title = element_text(size = 10),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 6),
    legend.position = "right",
    aspect.ratio = 1)
```

-   I can modify my colors to be accessible to anyone's eyes

```{r}
#| label: dvs-2-ex-2
# Lab 4 Question 8 (Revised to make it colorblind friendly)
ggplot(ca_childcare, aes(x = mhi_2018, 
                         y = mfcc_infant)) +
  geom_point(alpha = 0.5, color = "blue") +
  geom_smooth(method = "lm", color = "pink") +
  labs(
    title = "Relationship between median household income and infant childcare prices in California",
    x = "Median household income in 2018 ($)",
    y = "Median weekly price for infant care ($)") 
```

-   I can modify my plot titles to clearly communicate the data context

```{r}
#| label: dvs-2-ex-3
# Lab 4 Question 8
ggplot(ca_childcare, aes(x = mhi_2018, 
                         y = mfcc_infant)) +
  geom_point(alpha = 0.5, color = "green") +
  geom_smooth(method = "lm", color = "pink") +
  labs(
    title = "Relationship between median household income and infant childcare prices in California",
    x = "Median household income in 2018 ($)",
    y = "Median weekly price for infant care ($)") 

```

-   I can modify the text in my plot to be more readable

```{r}
#| label: dvs-2-ex-4
# Challenge 4 
plot <- ca_childcare |>
  pivot_longer(cols = c(mcsa,mfccsa),
              names_to = "type_of_care",
              values_to = "price") |>
  mutate(type_of_care = recode(type_of_care,
                              "mfccsa" = "Family Childcare (In-home)",
                              "mcsa" = "Center-based Care"))

ggplot(plot, mapping = aes(x = type_of_care, 
                         y = price)) +
  geom_boxplot(alpha = 0.5, color = "darkgreen") +
  labs(
    title = "Comparing the California weekly full-time median price 
for center-based childcare versus family (in-home)",
    x = "Type of childcare",
    y = "Full time median price ($)")+
  theme(plot.title = element_text(size = 15, face = "bold"),
        axis.title.x = element_text(size = 12),  
        axis.title.y = element_text(size = 12))
```

-   I can reorder my legend to align with the colors in my plot

```{r}
#| label: dvs-2-ex-5
#Challenge 2 Question 2
ggplot(data = surveys,
       mapping = aes( x = weight, y = species, color = sex)) +
  geom_jitter(height = 0.25, color = "darkgreen", alpha = 0.125)+
  geom_boxplot(outlier.shape = NA)+
  labs( x = "Species", y = NULL, title = "Rodent weight by species and sex", subtitle = "Weight (g)", legend = "Sex")+
  scale_color_manual(values = c("F" = "#ff00f8", "M" = "#0060d8"))

```

**DVS-3: I show creativity in my visualizations**

-   I can use non-standard colors (Example 1)

```{r}
#| label: dvs-3-1-ex-1
# Lab 4 Question 8 (Revised to make it colorblind friendly (as Dr.T advised) and use non standard colors)
ggplot(ca_childcare, aes(x = mhi_2018, 
                         y = mfcc_infant)) +
  geom_point(alpha = 0.5, color = "#1874CD") +
  geom_smooth(method = "lm", color = "#FF69B4") +
  labs(
    title = "Relationship between median household income and infant childcare prices in California",
    x = "Median household income in 2018 ($)",
    y = "Median weekly price for infant care ($)") 
```

-   I can use non-standard colors (Example 2)

```{r}
#| label: dvs-3-1-ex-2
# Challenge 2 (revised to use non standard colors)
ggplot(data = surveys,
       mapping = aes( x = weight, y = species, color = sex)) +
  geom_jitter(height = 0.25, color = "grey", alpha = 0.125)+
  geom_boxplot(outlier.shape = NA)+
  labs( x = "Species", y = NULL, title = "Rodent weight by species and sex", subtitle = "Weight (g)", legend = "Sex")+
  scale_color_manual(values = c("F" = "#ff00f8", "M" = "#0060d8"))
```

-   I can use annotations (e.g., `geom_text()`)

```{r}
#| label: dvs-3-2
# Lab 10 Question 13
binded |>
  slice_sample(n = 100) |>
  mutate(num = row_number()) |>
  ggplot(aes(y = num)) +
  geom_errorbarh(aes(xmin = ci_lower,
                     xmax = ci_upper,
                     color = population_slope),
                 height = 0.3, linewidth = 0.5) +

  geom_vline(xintercept = 0.5, linetype = "dashed") +  
  scale_color_manual(values = c("TRUE" = "steelblue", "FALSE" = "red"),
                     labels = c("TRUE" = "Contains β1", "FALSE" = "Misses β1"),
                     name = "population slope = 0.5") +
  labs(
    title = "95% Confidence Intervals of Estimated Regression Slope
for 100 Simulated Datasets",
    subtitle = "Cl's that do not include the population slope are highlighted in red",
    x = "Slope Coefficient Estimate",
    y = ""
  ) +
  theme(legend.position = "top")

```

-   I can choose creative geometries (e.g., `geom_segment()`, `geom_ribbon)()`)

```{r}
#| label: dvs-3-3
#Lab 4 Question 8
ggplot(ca_childcare, aes(x = mhi_2018, 
                         y = mfcc_infant)) +
  geom_point(alpha = 0.5, color = "green") +
  geom_smooth(method = "lm", color = "pink") +
  labs(
    title = "Relationship between median household income and infant childcare prices in California",
    x = "Median household income in 2018 ($)",
    y = "Median weekly price for infant care ($)") 

```

**DVS-4: I can calculate numerical summaries of variables.**

-   Example using `summarize()`

```{r}
#| label: dvs-4-summarize
# Lab 7 Question 2
fish |>
  summarise(across(everything(), ~sum(is.na(.x)))) |>
  pivot_longer(
    everything(),
    names_to = "variable",
    values_to = "number_of_missing_values") |>
  filter(number_of_missing_values > 0)
```

-   Example using `across()`

```{r}
#| label: dvs-4-across
# Lab 7 Question 2
fish |>
  summarise(across(everything(), ~sum(is.na(.x)))) |>
  pivot_longer(
    everything(),
    names_to = "variable",
    values_to = "number_of_missing_values") |>
  filter(number_of_missing_values > 0)
```

**DVS-5: I can find summaries of variables across multiple groups.**

-   Example 1

```{r}
#| label: dvs-5-1
# Lab 3 Question 6
teacher_evals_clean |>
  summarize( 
    count_uniq_teacher = n_distinct(teacher_id),
    count_uniq_course = n_distinct(course_id))
```

-   Example 2

```{r}
#| label: dvs-5-2
# Lab 3 Question 11
teacher_evals_clean |>
  filter(seniority == 1)|>
  group_by(teacher_id)|>
  summarise(
    avg_fail_rate = mean(percent_failed_cur, na.rm = TRUE),
    n_courses = n_distinct(course_id)
  )|>
  mutate(
    group_min = min(avg_fail_rate, na.rm = TRUE),
    group_max = max(avg_fail_rate, na.rm = TRUE)) |>
  filter(avg_fail_rate %in% c(group_min, group_max)) |>
  arrange(avg_fail_rate)
```

**DVS-6: I can create tables which make my summaries clear to the reader.**

-   I can modify my column names to clearly communicate the data context

```{r}
#| label: dvs-6-ex-1
# Lab 4 Question 5
med_income <- ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(region, study_year) |>
  summarise(median_income = median(mhi_2018, na.rm = TRUE), .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median_Household_Income_")|>
   arrange(desc(Median_Household_Income_2018))

```

-   I can modify the text in my table to be more readable (e.g., bold face for column headers)

```{r}
#| label: dvs-6-ex-2
# Lab 9 Question 3
surveys |>
  map_chr(typeof) |>      
  enframe(name = "Variable", 
          value = "Data Type") |>
  arrange(Variable) |> 
  kable(
    caption = "Classes of Variables in the surveys Dataset in alphabetical order",
    col.names = c("**Variable**", "**Class**")
  ) 

```

-   I can arrange my table to have an intuitive ordering

```{r}
#| label: dvs-6-ex-3
# Lab 4 Question 5
med_income <- ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(region, study_year) |>
  summarise(median_income = median(mhi_2018, na.rm = TRUE), .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_income,
              names_prefix = "Median_Household_Income_")|>
   arrange(desc(Median_Household_Income_2018))
```

**DVS-7: I show creativity in my tables.**

-   I can use non-default colors

```{r}
#| label: dvs-7-ex-1
# Lab 9 Question 8 (Revised to make colors non-default)
fish |>
  map_int(~ sum(is.na(.x))) |>
  enframe(name = "Measurement Variable", value = "Missing Values")|>
  arrange(`Measurement Variable`) |>
  gt() |>
  tab_header(
    title = "Number of Missing Values for Fish Measurements",
    subtitle = "Data Collected from 1989 to 2006 on the Blackfoot Fish River in Montana"
  ) |>
  data_color(
    columns = `Missing Values`,
    fn = function(x) {
      ifelse(
        x == 0, "#00CD00",  
        "#EE2C2C")
    }
  )
```

-   I can modify the layout of my table to be more readable (e.g., `pivot_longer()` or `pivot_wider()`)

```{r}
#| label: dvs-7-ex-2
# Lab 7 Question 2
fish |>
  summarise(across(everything(), ~sum(is.na(.x)))) |>
  pivot_longer(
    everything(),
    names_to = "variable",
    values_to = "number_of_missing_values") |>
  filter(number_of_missing_values > 0)
```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

-   using a single function call with multiple inputs (rather than multiple function calls)

```{r}
#| label: pe-1-one-call
# Challenge 3 Question 1
new_teacher_eval<- evals |>
  filter(question_no == 903) |>
  mutate(set_level = if_else(SET_score_avg >=4, "excellent", "standard"),
         sen_level = case_when(seniority <=4 ~ "junior",
                               seniority >=5 & seniority <=8 ~ "senior",
                               seniority >8 ~ "very senior"))|>
  select(course_id, set_level, sen_level)
```

-   using `across()`

```{r}
#| label: pe-1-across
# Lab 3 Question 5
evals |>
  rename(sex = gender)|>
  filter(no_participants >= 10)|>
  mutate(
    teacher_id = as.character(teacher_id),
    across(c(academic_degree, seniority, sex), as.factor)
  )|>
  select(course_id, teacher_id, question_no, no_participants, resp_share,
         SET_score_avg, percent_failed_cur, academic_degree, seniority, sex)
```

-   using functions from the `map()` family

```{r}
#| label: pe-1-map-1
# Lab 9 Question 7
fish |>
  map_int(~ sum(is.na(.x))) |>
  enframe(name = "Variable", value = "Number of Missing Values")
```

**PE-2: I can write functions to reduce repetition in my code.**

-   Example 1: Function that operates on vectors

```{r}
#| label: pe-2-1
# Lab 7 Question 4

rescale_01 <- function(x){
  
  if (!is.numeric(x)) {
    stop()
  }
  
  if (length(x) <= 1) {
    stop()
  }

  y <- range(x, na.rm = TRUE)
  
  x = (x -y[1]) / (y[2] - y[1])
}
```

-   Example 2: Function that operates on data frames

```{r}
#| label: pe-2-2
# Lab 8 Question 3
plot_function <- function(df, x, y) {
  
  
  ggplot(df, aes(x = {{ x }}, y = {{ y }}, color = {{ y }})) +
    geom_point() +
    labs(
      x = str_replace_all(rlang::as_label(rlang::enquo(x)),  "_", " "),
      y = str_replace_all(rlang::as_label(rlang::enquo(y)),  "_", " "),
      title = paste("Relationship between",
                    str_replace_all(rlang::as_label(rlang::enquo(x)),  "_", " "),
                    "and",
                    str_replace_all(rlang::as_label(rlang::enquo(y)),  "_", " ")),
      color = str_replace_all(rlang::as_label(rlang::enquo(y)),  "_", " ")
      )
   
}
```

-   Example 3: Function that operates on vectors *or* data frames

```{r}
#| label: pe-2-3
# Lab 8 Question 4

style_plot <- function(plot, theme_fn = theme_bw(), palette = RColorBrewer::brewer.pal(8, "Accent"), aesthetic = "fill") {
  
  if (!aesthetic %in% c("color", "fill")) {
    stop()
  }

  styled_plot <- plot + theme_fn
  
  if (aesthetic == "color") {
    styled_plot <- styled_plot + scale_color_manual(values = palette)
  } else {
    styled_plot <- styled_plot + scale_fill_manual(values = palette)
  }
  
  return(styled_plot)
}
```

**PE-3:I can use iteration to reduce repetition in my code.**

-   using `across()`

```{r}
#| label: pe-3-across
# Lab 8 Question 1
rescale_01 <- function(x){
  if (!is.numeric(x)) {
    stop()}
  if (length(x) <= 1) {
    stop()}
  y <- range(x, na.rm = TRUE)
  x = (x -y[1]) / (y[2] - y[1])
  }

rescale_column <- function(df, cols) {
  df |>
    mutate(across({{ cols }}, rescale_01))
  }
```

-   using a `map()` function with **one** input (e.g., `map()`, `map_chr()`, `map_dbl()`, etc.)

```{r}
#| label: pe-3-map-1
#  Lab 10 Question 10
funcdata <- map(.x = 1:1000,
              .f = ~ mycifun(beta0 = 3,
                             beta1 = 0.5,
                             n = 100)
              ) 
```

-   using a `map()` function with **more than one** input (e.g., `map_2()` or `pmap()`)

```{r}
#| label: pe-3-map-2
# Lab 10 Question 1
results <- map_int(.x = 1:10000,
                   .f = ~ randomBabies(4)
                  )
```

**PE-4: I can use modern tools when carrying out my analysis.**

-   I can use functions which are not superseded or deprecated

```{r}
#| label: pe-4-1
# Lab 3 Question 8 (Revised to update syntax)
teacher_evals_clean |>
  filter(if_any(everything(), ~ is.na(.x))) |>
  select(teacher_id, course_id, everything())
```

-   I can connect a data wrangling pipeline into a `ggplot()`

```{r}
#| label: pe-4-2
# Lab 10 Question 13
binded |>
  slice_sample(n = 100) |>
  mutate(num = row_number()) |>
  ggplot(aes(y = num)) +
  geom_errorbarh(aes(xmin = ci_lower,
                     xmax = ci_upper,
                     color = population_slope),
                 height = 0.3, linewidth = 0.5) +
  geom_vline(xintercept = 0.5, linetype = "dashed") +  
  scale_color_manual(values = c("TRUE" = "steelblue", "FALSE" = "red"),
                     labels = c("TRUE" = "Contains β1", "FALSE" = "Misses β1"),
                     name = "population slope = 0.5") +
  labs(
    title = "95% Confidence Intervals of Estimated Regression Slope
for 100 Simulated Datasets",
    subtitle = "Cl's that do not include the population slope are highlighted in red",
    x = "Slope Coefficient Estimate",
    y = ""
  ) +
  theme(legend.position = "top")
```

## Data Simulation & Statisical Models

**DSSM-1: I can simulate data from a *variety* of probability models.**

-   Example 1

```{r}
#| label: dsm-1-1
# Lab 10 Question 4

intercept = 2
slope = 1

x = runif(100, min = 0, max = 1)

ep = rnorm(100, mean = 0, sd = 1)

y = intercept + x*slope + ep

observed_data = tibble(x = x, y = y)

observed_data
```

-   Example 2

```{r}
#| label: dsm-1-2
# Lab 10 Question 8

mycifun <- function(beta0, beta1, n) {
  
  x  <- runif(n, min = 0, max = 1)         
  ep <- rnorm(n, mean = 0, sd = 1)         
  y  <- beta0 + beta1 * x + ep       
  
  observed_data <- tibble(x = x, y = y)
  
  linear <- lm(y ~ x, data = observed_data)
  
  est <- tidy(linear, conf.int = TRUE) |>
  filter(term == "x") 
  
  tibble(
    slope_est       = est$estimate,
    ci_lower        = est$conf.low,
    ci_upper        = est$conf.high,
    population_slope  = (beta1 >= ci_lower & beta1 <= ci_upper)
  )
}
```

**DSSM-2: I can conduct common statistical analyses in R.**

-   Example 1

```{r}
#| label: dsm-2-1
# Lab 1 Question 9
t.test(len ~ supp,
       data = ToothGrowth,
       var.equal = TRUE)
```

-   Example 2

```{r}
#| label: dsm-2-2
# Lab 2 Question 17
species_mod <- aov(weight~species, data = surveys)
```

-   Example 3

```{r}
#| label: dsm-2-3
# Lab 4 Question 9 
reg_mod1 <- lm(mfcc_infant ~ mhi_2018, data = ca_childcare)
```

## Revising My Thinking

<!-- How did you revise your thinking throughout the course? How did you revise your thinking on the code examples you have provided in your portfolio? -->

<!-- For the revisions included in your Portfolio, to help me understand the nature of your revisions, please denote somehow the feedback I provided you (e.g., boldface, italics, colored text) before your revisions. -->

I took in feedback from both Dr. T's code rubric as well as code reviews from my peers, to revise my thinking throughout the course. I kept an open mind, and read articles relating to functions that I didn't really understand in class to understand how to write my code in the most effective and concise way. When doing revisions for my code, I try to figure out where my thought process went wrong while writing the code, and then revised my code according to the feedback I received. I listen to feedback and try to reflect what I learnt in future code, which I think is important to growing in this class.

## Extending My Thinking

<!-- How did you extended your thinking throughout the course? How did you extend your thinking on the code examples you have provided in your portfolio? -->

I've extended my thinking in this class by reading other sources besides the ones provided to better understand certain functions used in the class, as well as try to incorporate what I learnt into future assignments, and trying to use feedback I get to make my code better than I thought it could be, using functions that I wasn't comforatable using yet.

## Peer Support & Collaboration

<!-- Include an image or a description of feedback you gave that you are proud of (either in a peer review or in Discord). -->

<!-- Include a description of how you grew as a collaborator through the weekly pair programming activities.   -->

"I love that you included comments in your code chunks to describe what the code does! Your code is also very tidy. I would put the answers to the question right after it, before your code chunks that support your answer, it might make it easier to read." Was one of the reviews I was proud of, and that's because I felt like I was being a supportive peer while also giving some feedback, their code and the formatting of the code looked good to me, the only thing was where the answer went, because I think it's easier for readers to see an answer before seeing the explanation to understand the question better.

Through the weekly programming activities, I grew as a collaborator by being able to better communicate my ideas as well as being a better listener and listening to other people's ideas. I've always been more used to the discussion type collaboration, but this way of collaborating really helped me understand the other person's thought process and I think I learnt a lot from it.
